Proportional multi-state multiple-cohort life table model

### 2018-04-03 MSLT/MSLTdoc.Rmd
Adding table with PMSLT inputs

```{r, echo=FALSE}
inputs <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18)
colnames(inputs) <- c("Life table","Source","Comments")
rownames(inputs) <- c("Population", "All-cause mortality", "Total YLD rate", "Incidence", "Case fatality", "Disability weight")
inputs <- as.table(inputs)
inputs
```

>>>>

```{r, echo=FALSE}
pmslt_inputs <- matrix(c(1:15), ncol = 3, byrow = TRUE)
colnames(pmslt_inputs) <- c("Input", "Source", "Comments")
rownames (pmslt_inputs) <- c("Population numbers", "Death rates", "Years lived with disability rates", "Disease epidemilogy", "Disability weights")
print(pmslt_inputs)
```
